Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2018-09-12 analysis/paper/sim_survey_paper.Rmd
Minor tweaks of presentation, paper and data export for Geoff

Next discuss trend...

@@

abun_plot <- ggplot() +
  geom_path(data = df_strat, aes(x = long, y = lat, group = group), 
            color = "grey", size = 0.05) +
  geom_path(data = df_lines, aes(x = long, y = lat, group = group, color = level),
            size = 0.3) +
  scale_color_viridis(labels = labs, discrete = TRUE, name = "N") + 
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0)) +
  coord_equal() +
  theme_void() + guides(color = guide_legend(keywidth = 0.4, keyheight = 0.25, 
                                             default.unit = "cm", ncol = 1)) +
  theme(legend.justification = c(0, 1),
        plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"))

setdet <- sim$setdet
setdet <- setdet[setdet$year == which_year & setdet$sim == which_sim, ]

set_plot <- ggplot() +
  geom_path(data = df_strat, aes(x = long, y = lat, group = group), 
            color = "grey", size = 0.05) +
  geom_point(data = setdet, aes(x = x, y = y, size = n, color = n), alpha = 0.8) +
  scale_size_area(name = "   n", max_size = 10, breaks = pretty(setdet$n, 8)) +
  scale_color_viridis(name = "   n", breaks = pretty(setdet$n, 8)) + 
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0)) +
  coord_equal() +
  theme_void() + guides(color = guide_legend(keywidth = 0.4, keyheight = 0.2, default.unit = "cm")) +
  theme(legend.justification = c(0, 1),
        plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"))

>>>>

### TODO

- Next discuss trend...
- Look into the ictopelagic sampling design literature (suggestion from Pierre)
- Mention that simulation is an approach widely applied to inform sampling design (program MARK, distance, RandomForest, etc.); i.e. cite the gods
- Look into work done on occupancy modeling and sampling design for such studies (i.e. book suggestion by Aaron)

@@

abun_plot <- ggplot() +
  geom_path(data = df_strat, aes(x = long, y = lat, group = group), 
            color = "grey", size = 0.05) +
  geom_path(data = df_lines, aes(x = long, y = lat, group = group, color = level),
            size = 0.3) +
  scale_color_viridis(labels = labs, discrete = TRUE, name = "N") + 
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0)) +
  coord_equal() +
  theme_void() + guides(color = guide_legend(keywidth = 0.4, keyheight = 0, 
                                             default.unit = "cm", ncol = 1)) +
  theme(legend.justification = c(0, 1),
        plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"))

setdet <- sim$setdet
setdet <- setdet[setdet$year == which_year & setdet$sim == which_sim, ]
breaks <- pretty(setdet$n, 7)

set_plot <- ggplot() +
  geom_path(data = df_strat, aes(x = long, y = lat, group = group), 
            color = "grey", size = 0.05) +
  geom_point(data = setdet, aes(x = x, y = y, size = n, color = n), alpha = 0.8) +
  scale_size_area(name = "   n", max_size = 10, limits = range(breaks), breaks = breaks) +
  scale_color_viridis(name = "   n", limits = range(breaks), breaks = breaks) + 
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0)) +
  coord_equal() +
  theme_void() + guides(color = guide_legend(keywidth = 0.4, keyheight = 0.2, default.unit = "cm")) +
  theme(legend.justification = c(0, 1),
        plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"))

### 2018-09-12 analysis/presentation/sim_survey_presentation.Rmd
Minor tweaks of presentation, paper and data export for Geoff

---
title: "Using simulation to optimize the sampling design of fisheries-independent trawl surveys"
author: "Paul M. Regular & Fran Mowbray"
date: "September 12^th^, 2018"
output:
  ioslides_presentation:
    mathjax: local
    self_contained: false
    widescreen: true
    incremental: true
    logo: dfo_logo.png
    css: dfo_style.css
bibliography: references.bib
---

@@

- Taylor to other species and assess sampling protocol
- Add a time component to assess trade-offs / efficiency
- Assess the effects of
    - Missing strata
    - Variable trawl area
    - Random vs. stratified age sampling
- Use this as a platform to test spatial models
- Use as an operating model for an MSE
- Others?

>>>>

---
title: "Using simulation to optimize the sampling design of fisheries-independent trawl surveys"
author: "Paul M. Regular & Fran Mowbray"
date: "September 12^th^, 2018"
output:
  ioslides_presentation:
    widescreen: true
    incremental: true
    logo: dfo_logo.png
    css: dfo_style.css
bibliography: references.bib
---

@@

- Tailor to other species and assess sampling protocol
- Add a time component to assess trade-offs / efficiency
- Assess the effects of
    - Missing strata
    - Variable trawl area
    - Random vs. stratified age sampling
- Use this as a platform to test spatial models
- Use as an operating model for an MSE
- Others?
